\section{Introduction}
\label{sec:intro}

\monika{i made some significant changes in this section, please check}

The Milky Way has a massive, compact object at its center that is most likely a supermassive black hole \citep{2019Sci...365..664D, 2019A&A...625L..10G}.
The supermassive object is surrounded by an accretion flow\footnote{where the accretion flow may consists of plasma inflow, wind-like outflow and a collimated jet} visible across 17 decades in frequency of electromagnetic spectrum.
Hereafter, we will use \sgra to refer to the supermassive black hole candidate, accretion flow, and its emission.

\sgra is one of the most frequently observationally and theoretically studied systems.
%We refer the reader to \citetalias{PaperII} and \citetalias{PaperIII} of this series for a comprehensive overview of historical and recent observations of the source.
The main characteristic of the \sgra system is its extremely low overall luminosity with respect to the Eddington limit.
The low luminosity suggests that matter falls onto \sgra's central object in the form of a radiatively inefficient/advection dominated accretion flow (RIAF/ADAF, as proposed by \citealt{1977ApJ...214..840I,1994ApJ...428L..13N, 1995ApJ...444..231N, 1995ApJ...452..710N, 1996A&AS..120C.287N, 1998ApJ...492..554N,2014ARA&A..52..529Y}) rather than in form of a thin disk \citep{1973A&A....24..337S}.
Since the nearly flat spectrum emitted by \sgra in radio is similar to radio spectra observed in jets from Active Galactic Nuclei, it has been also suggested that the majority of the \sgra emission could be in fact produced by a jet launched by an accreting black hole rather than matter falling onto the black hole event horizon \citep{2000A&A...362..113F}.
% 2000A&A...362..113F,2004A&A...414..895F, 2005ApJ...635.1203M, 2013A&A...559L...3M
The jet scenario in \sgra is further supported by time lags observed between emission measured at multiple radio frequencies \citep{2021arXiv210713402B}.

It's been established that most of the \sgra emission is produced in synchrotron process so the source model requires description of plasma and magnetic field configuration.
Models of magnetized RIAFs/ADAFs have been constructed using semi-analytic prescriptions \citep[e.g.,][]{1995Natur.374..623N,2000ApJ...541..234O, 2009ApJ...697...45B,2011ApJ...735..110B} and using time-dependent General Relativistic Magnetohydrodynamics (GRMHD) simulations \citep[e.g.,][]{2000ApJ...528..462H, 2003ApJ...589..458D, 2003ApJ...589..444G, 2007CQGra..24S.235G, 2012ApJS..201....9F, 2014ApJ...796...22F, 2016ApJS..225...22W, 2017ApJS..231...17A, 2018JPhCS1031a2008O, 2019A&A...629A..61O, 2019ApJS..243...26P}.
Semi-analytic RIAF/ADAF models typically do not include relativistic jets or outflows, but those are naturally produced in GRMHD simulation and contribute to the observed emission. GRMHD simulations also naturally produce variability that is observed in \sgra at multiplewavelents.
{\bf DRAFT: The GRMHD simulations of ADAFs have also revealed that ADAF-like accretion solutions are
not unique. In particular one can distinguish two dramatically different ADAFs modes: standard and normal evolution (SANE) mode, in which magnetic field pressure is weaker than plasma pressure and magnetic fields are turbulent or magnetically arrested disks (MADs), in which magnetic fields are strong and organized and can even disrupt accretion.
The outstanding questions about ADAF/RIAF in \sgra are: what is the exact geometry and strength of its magnetic fields, what is the energy distribution of electrons in accretion flow, how is this distribution function reflecting plasma microphysical effects and do the microphysical effects naturally lead to jet being brighter than the accretion disk; what drives the observed variability of the source and finally is the \sgra central black hole spinning. Previously published GRMHD models of \sgra generically predict source sizes at millimeter wavelengths consistent with observational data (e.g., \citealt{2008Natur.455...78D}, Moscibrodzka+2009, Dexter+2009);
%(the first proto-EHT, non-imaging detections of \sgra are reported by \citealt{2008Natur.455...78D, 2015Sci...350.1242J} and \citealt{2018ApJ...859...60L}).
the radio spectral shape is best described by jet emission (e.g., Moscibrodzka \& Falcke 2013, Ressler+2017), and the source linear polarization requires strongly magnetized flow or non-thermal electrons (Johnson+2-17, Gold +2017, Dexter+2020). Near event horizon variability can be produced by a turbulence (Dexter+2010), lensing events (Chan+2015), or magnetic flux eruptions associated with MAD flow (e.g., Tchekhovskoy+2011). The 86 GHz data seem to require non-thermal electrons (Chael+2018, Issaoun+2019). }

The major difficulty in determining the exact nature of \sgra radio emission is caused by an interstellar scattering screen that distorts our view of the Galactic Center up to $\lambda \sim 1\mm$ wavelengths
%\citep{2016ApJ...824...40O, 2017MNRAS.471.3563D, 2018ApJ...865..104J, 2019A&A...621A.119B}
\citep[see][and references therein]{2018arXiv180501242P, 2018ApJ...865..104J,2019ApJ...871...30I}.
%The daily flaring activity of \sgra, observed at higher energies in near infra-red and x-rays \citep[e.g.,][]{2009ApJ...698..676D, 2019ApJ...886...96H}, suggests that conditions around the supermassive black hole occasionally favor electron acceleration.
%\citep{2000ApJ...541..234O,2020MNRAS.494.5923P} \br{here we are missing many citations, at least to Ponti+2019 and a few papers by Dodds-Eden, but likely more, including Ripperda+2020 and Ripperda+2021}\monika{we dont want to overload this paper with observational papers since this is all better described in paper II and III, will cite theoretical work, no problem}
% it is not critical to cite theory work here
%However, these observations do not discriminate between source models because they do not have sufficient resolution. Hence, the existing models for \sgra emission remain weakly constrained (\note{a few essential references}).
%\citep[see e.g.,][]{2005ApJ...621..785G,2006MNRAS.370..219M,2007A&A...474....1M, 2007MNRAS.379.1519M,2007ApJ...671.1696S, 2009A&A...508L..13M,2009ApJ...701..521C, 2009ApJ...706..497M, 2012ApJ...746L..10D,2012MNRAS.421.1315Z, 2012ApJ...755..133S, 2013A&A...559L...3M, 2014A&A...570A...7M,  2015ApJ...812..103C,2015ApJ...799....1C,2016A&A...588A..57F,2016ApJ...826...77B, 2016ApJ...831....4P, 2016MNRAS.455.2187M,2017ApJ...837..180G, 2017ApJ...844...35M, 2017ApJ...851..148M,2017MNRAS.467.3604R, 2018A&A...612A..34D, 2018ApJ...856..163M,2018ApJ...863..148P,2018JCAP...07..015H, 2018MNRAS.478.1875J,2018MNRAS.478.5209C,  2019ApJ...884..148B, 2020ApJ...896L...6R, 2020ApJ...897...99T, 2020MNRAS.492.3272R,2020MNRAS.493.1404A, 2020MNRAS.494.4168D,2020MNRAS.497.4999D, 2020ApJ...896L...6R, 2021ApJ...917....8B,2021MNRAS.502.2023P,2021arXiv210105327E}.
%\br{also here we are missing Chatterjee+2021; Scepi+2021; Ripperda+2020; Ripperda+2021 and also Nathanail+2020 and Nathanail+2021 and Chashkina+2021}
%alma lightcurves papers \citep{2014ApJ...790....1B,2015ApJ...802...69B,  2018ApJ...868..101B,2019ApJ...881L...2B}
%\ckc{It's good to be inclusive in citations but we need to make the intro readable.  I suggest only keep the i) first few, ii) ``classic'', and iii) review papers in the intro, and say things ``see ... and reference therein''.  Citation of EHT members' newer work can then be moved into the model description sections.}\monika{agree}
The Event Horizon Telescope (EHT) is a very-long-baseline interferometric (VLBI) experiment operating at $230\GHz$ or wavelength $\lambda = 1.3\mm$
(see \citealt{M87PaperII}, hereafter \citetalias{M87PaperII}, for the instrument introduction).
EHT operates at high enough frequency to penetrate the scattering screen, with angular resolution sufficient to directly image structures in the immediate vicinity of the black hole event horizon.
In April~2017, the EHT observed \sgra (among other sources, including the core of the M87 galaxy, see \citealt{M87PaperI}, hereafter \citetalias{M87PaperI}) and produced the first ever horizon scale images of the source.
We report the results of these observations in \citetalias{PaperII} and \citet{PaperIII}, hereafter \citetalias{PaperIII}, and characterize the basic properties of the emission visible in the EHT images in \citetalias{PaperIV}.
The main goal of the present paper \citepalias{PaperV} is to provide the first comprehensive physical interpretation of the EHT~2017 \sgra datasets.

The paper is structured as follows.
In Section~\ref{sec:models}, we begin with a description of our main assumptions, one-zone source models, and a standard simulation library used to model near horizon emission from the \sgra system.
Our library of theoretical models assumes that general relativity is valid and the spacetime around \sgra is described by a Kerr spacetime \citep{1963PhRvL..11..237K}.
A full discussion of \sgra observations in the context of alternative theories of gravity can be found in an accompanying paper, \citet{PaperVI}, hereafter \citetalias{PaperVI}.
Our model library is based on time-dependent GRMHD simulations that, combined with general relativistic radiative transfer models, result in images and broadband spectra of the models.
The library of simulated images was used in \citetalias{PaperIII} and \citet{PaperIV}, hereafter \citetalias{PaperIV}, to validate the \sgra EHT imaging and parameter estimation algorithms.
In Section~\ref{sec:observations}, we gather the standard observational datasets that are used in the present work to test theoretical models of \sgra.
These datasets comprise a subset of EHT~2017 observations and other non-EHT historical or other data.
All future theoretical studies can use this information to test their theories.
In Section~\ref{sec:comparisons}, we describe model scoring procedures and use a large number of the source models to infer physical properties of \sgra system.
We discuss the model limitations, results in the context of previous studies and outlook into future \sgra theoretical research directions in Section~\ref{sec:discussions}.
Finally, we conclude in Section~\ref{sec:conclusions}.

This paper is supplemented with several appendices.
In Appendix~\ref{app:tables},      we summarize theoretical models used in this work in the form of tables and figures.
In Appendix~\ref{app:numerical},   we discuss important numerical details of our simulations.
In Appendix~\ref{app:variability}, we discuss the impact of physical effects on the variability of the models.
