\documentclass[twocolumn,twocolappendix,tighten,dvipsnames,linenumbers]{aastex63}
\usepackage{eht}

\NewPageAfterKeywords

% Inline comments
\newcommand\note[1]{{\color{OliveGreen}[note: #1]}}
\newcommand\ckc[1]{{\color{MidnightBlue}[ckc: #1]}}
\newcommand\hyp[1]{{\color{Salmon}[HYP: #1]}}
\newcommand\monika[1]{{\color{Orange}[MM: #1]}}

%==============================================================================
\begin{document}

\title{First Sagittarius A* Event Horizon Telescope Results. V.\\
  Constraining the Astrophysical Properties of the Galactic Center Black Hole}
\shorttitle{First \sgra EHT Results on Astrophysics}

\author{Event Horizon Telescope Collaboration et al.}
\shortauthors{EHT Collaboration et al.}

\submitjournal{ApJL}

\received{\today}
\revised{\today}
%\accepted{\today}

\begin{abstract}
  We present theory interpretations of the accretion flow around the
  supermassive black hole Sagittarius A* (\sgra) using the Event
  Horizon Telescope (EHT) observation at 1.3\,mm collected during the
  2017 April 5--11 observing campaign.

  \color{BrickRed}

  [This is EHT's \sgra paper V.
  We are at the position to turn this from a sketchpad to an actual
  draft of the paper.
  The original draft is backed up in the \texttt{2018-08-01/}
  directory on Overleaf.

  For adding references, simply cite the ADS key, e.g.,
  \texttt{\textbackslash citep\{2019ApJ...875L...5E\}}.
  The bash script \texttt{tools/adsbib.sh} would automatically pull
  the full BibTeX database from ADS.
  See \texttt{Makefile} to learn how to use the scripts in
  \texttt{tools/}.]
\end{abstract}

\keywords{galaxies: individual: \sgra -- Galaxy: center -- black hole
  physics -- techniques: high angular resolution -- techniques: image
  processing -- techniques: interferometric}

\tableofcontents

\clearpage

%==============================================================================
\section{Introduction}

The scientific goals and legacies of this paper may include:
\begin{itemize}
\item Description of a standard simulation library that is used in EHT's
  first \sgra papers (the ``GRMHD'' test set for imaging and calibration sets for
  MCFE and gravity) and subsequent papers (e.g., future papers that dive in the origin of
  variabilities).
\item Providing the first estimate on uncertainties in theoretical
  modelings by comparing models from different realizations/groups in
  similar parameter space.
\item Using the large number of models to extract theory-backed and
  statistical significant trends.
  E.g., edge-on images are more asymmetric.
\item Gathering a standard observation data set that \emph{all future}
  theoretical studies can use to test their models.
\item Providing the first theoretical/numerical interpretation of the
  EHT \sgra VLBI observation, with helps from historical data.
  This should include ``scores'' of the standard model sets and a few
  best bet models.
\item Summary of what models do not work and explain why.
\item Summary of what models work and their implications and
  limitations.
\item Outlook into future theoretical research directions, i.e.,
  importance of variability and viscosity, uncertainty in plasma
  models, etc.
\end{itemize}

\clearpage

%==============================================================================
\section{Astrophysical Models}

Many of them have the common assumption that \sgra is a black hole
described by the Kerr metric, with mass $\mbh$ and dimensionless spin
$\abh$ within the range $-1 < \abh < 1$.
Here $\abh \equiv Jc/G\mbh^2$, where $J$, $G$, and $c$ are the black
hole angular momentum, gravitational constant, and speed of light,
respectively.
We follow the convention of \citetalias{2019ApJ...875L...5E} that
$\abh < 0$ indicate anti-aligned angular momentum between the
accretion flow and that of the black hole.
\note{Describe other details of the current standard \sgra mode, e.g.,
  thick SANE or MAD accretion disks without tilted, etc.
  Describe main controversy in theory/model, e.g., disk vs jet.}

...

We adopted a weighted mean of \citet{2019Sci...365..664D} and
\citet{2019A&A...625L..10G} and fix the mass of \sgra to
\begin{align}
  \mbh &= (4.136 \pm 0.014) \times 10^6 \msun,\\
  D    &= (8.142 \pm 0.023) \kpc.
\end{align}
\note{The \sgra parameter memo indicates that there's no errors in the
  $M/D$ measurements.
  The errors for $M$ and $D$ don't seem consistent.
  Need to check with the parameter definition working group.}

...

%------------------------------------------------------------------------------
\subsection{One-Zone Model and Estimate}

Using the above mass and distance, the implied characteristic length
is $G\mbh/c^2 = 6.1 \times 10^{11}\cm$, characteristic time is
$G\mbh/c^3 = 20.4 \sec$, angular scale is $G\mbh/(c^2 D) = 5.03\uas$.
The radius of the shadow is $26.1\uas$.

Then
$ \nu L_\nu
= 4 \pi D^2 \nu F_\nu
= 1.8 \times 10^{34} (D/8127 \pc)^2 \times\allowbreak
  (\nu/230 \GHz)(F_\nu/{\rm Jy}) \erg \sec^{-1}$.
The Eddington luminosity for \sgra is
$ L_\mathrm{Edd}
= 4\pi G\mbh c/\kappa_{es}
= 5.2 \times 10^{44}\allowbreak\erg\sec^{-1}$.
The Eddington accretion rate is
$ \dot\mbh_\mathrm{Edd}
\equiv L_\mathrm{Edd}/(0.1 c^2)
= 5.8 \times 10^{24} \gm \sec^{-1}
= 0.09 \msun \yr^{-1}$.
The Eddington ratio is
$ L_\mathrm{bol}/L_\mathrm{Edd}
= 1.9 \times 10^{-10} (L_\mathrm{bol}/10^{35})$.

Next we consider a one zone model for \sgra.
The model consists of a single temperature sphere with magnetic field
oriented at $\pi/3$ to the line of sight.
Assumed flux is $2\Jy$, which is the average flux for \sgra measured
by ALMA during the 2017 campaign.
The sphere radius is
$5 G\mbh/c^2$.
The ratio of ion to electron temperature
$R \equiv T_i/T_e = 3$.
Assumed plasma
$\beta \equiv P_{gas}/(B^2/(8\pi)) = 1$,
electron temperature
$\Theta_e \equiv k T_e/(m_e c^2) = 10$.

The one zone model flux density is
\begin{align}
  F_\nu = \int I_\nu \, d\Omega =
  \frac{2 k T_e \nu^2}{c^2 D^2} \int dx dy\,\left[1-\exp(-\tau_\nu(x,y)\right]
\end{align}
where $d\Omega$ is a differential solid angle, $x$ and $y$ are
coordinates on the source plane in the same units as $D$, and
$\tau_\nu(x,y) = 2 \alpha_\nu (G\mbh/c^2) \sqrt{X_0^2 - X^2}$,
where $X$ is the offset on the sky from the center of the sphere in
units of
$GM/c^2$, and $X_0 = 5 G\mbh/c^2$.
Finally, $\alpha_\nu$ is the thermal synchrotron absorption
coefficient (units: $\cm^{-1}$).
The density is adjusted until the flux density is $2\Jy$.

For a pure hydrogen model, resulting parameters are: $n_e = 1.1 \times
10^6$, $B = 30\,\mathrm{G}$, $\tau_I = 0.48$, $\tau_Q = 0.35 $,
$\tau_V = 0.27$, Thomson depth $\tau_e = 5 G\mbh/c^2 \sigma_T = 2.2
\times 10^{-6}$, Compton $y = \tau_e 16 \Theta_e^2 = 3.6 \times
10^{-3}$, synchrotron cooling time is $t_{cool} = 3.1 \times 10^4\sec
= 1.5 \times 10^3 G\mbh/c^3$.

There is reason to believe that, if \sgra is fed by stellar winds as
in \citet{2019MNRAS.482L.123R}, the inflowing plasma is almost pure
helium.
In this case the results change only slightly; the cooling time drops
slightly because the rest-mass density (and therefore field strength)
per electron increases.

%------------------------------------------------------------------------------
\subsection{Semi-Analytical Accretion Models}

...

\subsubsection{RIAF Model}

...

\subsubsection{RIAF+Jet Model}

...

%------------------------------------------------------------------------------
\subsection{Numerical Models of the Inner Accretion Flows}

...

\begin{deluxetable*}{cccccccccc}
\tabletypesize{\footnotesize}
\tablehead{
  & \colhead{Spacetime} & \multicolumn{3}{c}{Fluid} & \multicolumn{2}{c}{Plasma} & \multicolumn{2}{c}{Camera} & \colhead{Note} \\
  \colhead{Name} &
  \colhead{$a_\mathrm{spin}$} &
  \colhead{Flux} & \colhead{$\Gamma$} & \colhead{$t_\mathrm{final}$ [$M$]} & % 3 fluid input
  \colhead{$\rho_0$} &
  \colhead{$R_\mathrm{high}$} & % 1 plasma input
  \colhead{Inclination $i$ [$^\circ$]} &
  \colhead{Realizations} &
  \colhead{Reference}
}
\startdata
Illinois  Thermal & 0, $\pm1/2$, $\pm15/16$ & MAD, SANE  & $5/3$ & 30,000 & 3 & 1, 10, 40, 160 & 10, 30, ..., 170 & 1080 & This work \\
Frankfurt Thermal & 0, $\pm1/2$, $\pm15/16$ & MAD, SANE  & $5/3$ & 30,000 &   & ...            &                  &      & This work \\
HAMR      Thermal & 0, $\pm1/2$, $\pm15/16$ & MAD, SANE  & $5/3$ & 30,000 &   & ...            &                  &      & This work \\
\hline
Frankfurt Nontheraml (powerlaw) & 0, $\pm1/2$, $\pm15/16$ & MAD,SANE  & $5/3$ & 30,000 & & & & & This work \\
HAMR      Nontheraml (powerlaw) & 0, $\pm1/2$, $\pm15/16$ & MAD,SANE  & $5/3$ & 30,000 & & & & & This work \\
\hline
Frankfurt Nontheraml ($\kappa$) & 0, $\pm1/2$, $\pm15/16$ & MAD,SANE  & $5/3$ & 30,000 & & & & & This work \\
HAMR      Nontheraml ($\kappa$) & 0, $\pm1/2$, $\pm15/16$ & MAD,SANE  & $5/3$ & 30,000 & & & & & This work \\
\hline
Critical $\beta$ & & & & & & & & \\
Stellar Wind Accretion & 0 & Stellar Wind & ? & & & & & \\
Koral Long & \!\!\!\!\!\!0, $\pm0.3$, $\pm0.5$, $\pm0.7$, $\pm0.9$\!\!\!\!\!\! & MAD & ? & 100,000 & & & & & \\
Tilted & ? & ? & ? & ? & & & & & Tilts at ...$^\circ$ \\
\enddata
\caption{Summary of numerical models used in this paper.}
\label{tab:parameters}
\end{deluxetable*}

%..............................................................................
\subsubsection{Thermal Model}

...

\paragraph{Illinois Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$: 0, $\pm1/2$, $\pm15/16$
\item Magnetic Flux: MAD, SANE
\item Adabatic Index $\Gamma$: 5/3
\item Time $t_\mathrm{final}$: 30,000$M$
\item $\rho_0$: 3 different density normalization chosen for each parameter set for $t \in [15,000, 20,000), [20,000, 25,000), [25,000, 30,000)$.
\item $R_\mathrm{high}$: 1, 10, 40, 160
\item Inclincation $i$: 10$^\circ$, 30$^\circ$, 50$^\circ$, ..., 170$^\circ$
\item Reference: this work
\item Status: w4 and w5 all done; w5 in progress
\end{itemize}

\paragraph{Frankfurt Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$: 0, $\pm1/2$, $\pm15/16$
\item Magnetic Flux: MAD, SANE
\item Adabatic Index $\Gamma$: 5/3
\item Time $t_\mathrm{final}$:
\item $\rho_0$:
\item $R_\mathrm{high}$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

\paragraph{HAMR Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$: 0, $\pm1/2$, $\pm15/16$
\item Magnetic Flux: MAD, SANE
\item Adabatic Index $\Gamma$:
\item Time $t_\mathrm{final}$:
\item $\rho_0$:
\item $R_\mathrm{high}$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

%..............................................................................
\subsubsection{Non-thermal (power-law )Models}

...

\paragraph{Frankfurt Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$: 0, $\pm1/2$, $\pm15/16$
\item Magnetic Flux: MAD, SANE
\item Adabatic Index $\Gamma$:
\item Time $t_\mathrm{final}$:
\item $\rho_0$:
\item Power law fraction $f$:
\item Power law index $p$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

\paragraph{HAMR Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$: 0, $\pm1/2$, $\pm15/16$
\item Magnetic Flux: MAD, SANE
\item Adabatic Index $\Gamma$:
\item Time $t_\mathrm{final}$:
\item $\rho_0$:
\item Power law fraction $f$:
\item Power law index $p$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

%..............................................................................
\subsubsection{Non-thermal ($\kappa$) Models}

...

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$: 0, $\pm1/2$, $\pm15/16$
\item Magnetic Flux: MAD, SANE
\item Adabatic Index $\Gamma$:
\item Time $t_\mathrm{final}$:
\item $\rho_0$:
\item $\kappa$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

\paragraph{Frankfurt Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$: 0, $\pm1/2$, $\pm15/16$
\item Magnetic Flux: MAD, SANE
\item Adabatic Index $\Gamma$:
\item Time $t_\mathrm{final}$:
\item $\rho_0$:
\item $\kappa$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

\paragraph{HAMR Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$: 0, $\pm1/2$, $\pm15/16$
\item Magnetic Flux: MAD, SANE
\item Adabatic Index $\Gamma$:
\item Time $t_\mathrm{final}$:
\item $\rho_0$:
\item $\kappa$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

%..............................................................................
\subsubsection{Critical $\beta$ Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$:
\item Magnetic Flux: MAD, SANE
\item Adabatic Index $\Gamma$:
\item Time $t_\mathrm{final}$:
\item $\rho_0$:
\item Power law fraction $f$:
\item Power law index $p$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

%..............................................................................
\subsubsection{Stellar Wind Accretion Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$: 0
\item Magnetic Flux: MAD, SANE
\item Adabatic Index $\Gamma$:
\item Time $t_\mathrm{final}$:
\item $\rho_0$:
\item Power law fraction $f$:
\item Power law index $p$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

%..............................................................................
\subsubsection{Koral Long MAD Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$: 0, $\pm0.3$, $\pm0.5$, $\pm0.7$, $\pm0.9$
\item Magnetic Flux: MAD
\item Adabatic Index $\Gamma$:
\item Time $t_\mathrm{final}$: 100,000$M$
\item $\rho_0$:
\item Power law fraction $f$:
\item Power law index $p$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

%..............................................................................
\subsubsection{Tilted Models}

% Please fill in basic information of the model in the following list.
% Please add more details if necesssary. A full paragraph description
% of the model is welcome, but not required at this point.
\begin{itemize}
\item $a_\mathrm{spin}$:
\item Magnetic Flux:
\item Adabatic Index $\Gamma$:
\item Time $t_\mathrm{final}$:
\item $\rho_0$:
\item Power law fraction $f$:
\item Power law index $p$:
\item Inclincation $i$:
\item Reference:
\item Status:
\end{itemize}

%------------------------------------------------------------------------------
\subsection{Scattering Models}

\clearpage

%==============================================================================
\section{Observational Constraints}

\subsection{Standard Measurement and Assumptions}

\subsection{EHT Observations}
\subsubsection{230\,GHz Light Curve Variability}
\subsubsection{230\,GHz VLBI Null Locations}
\subsubsection{230\,GHz VLBI Pre-Image Size}
\subsubsection{230\,GHz VLBI Ring Size}
\subsubsection{230\,GHz VLBI Ring Thickness}
\subsubsection{230\,GHz VLBI Ring Asymmetry}

\subsection{Non-EHT Observations}
\subsubsection{86\,GHz Flux}
\subsubsection{86\,GHz Image Size}
\subsubsection{NIR (Non-Overproduction) Constraints}
\subsubsection{X-ray (Non-Overproduction) Constraints}

\clearpage

%==============================================================================
\section{Comparisons}

\subsection{EHT Constraints}

\subsection{Non-EHT Constraints}

\subsection{Discussions}

\subsection{Caveats and Limitations}

\clearpage

%==============================================================================
\section{Conclusions}

\subsection{MAD vs SANE}

\subsection{Jet vs Disk}

\subsection{Electron Temperature}

\subsection{Inclination}

\subsection{Black Hole Spin}

\clearpage

%==============================================================================
\facility{EHT} \software{\ehtim, \difmap, \smili, \dmc, \themis, \foci}

%==============================================================================
\appendix

\section{Pass/Fail Tables}

\clearpage

%==============================================================================
\section{Numerical Details}

\subsection{GRMHD Resolution and Convergence}

\subsection{Image Resolution and Field of View}

\subsection{Samping SED}

\subsection{Fast Light vs Light-Speed Light}

\clearpage

%==============================================================================
\bibliographystyle{yahapj}
\bibliography{main,EHTCPapers}

%==============================================================================
\end{document}
